\normalfont \LARGE Improved Quasi-Static Methods for Time-Dependent Neutron Diffusion and Implementation in Rattlesnake

### 2016-12-20 doc/Thesis_proposal/thesis_proposal.tex
Addressing final MS proposal comments

These techniques are by no means an exhaustive list of the possible iteration techniques for IQS. Dulla et al. in \cite{Dulla2008} does an in depth analysis of the fixed point iteration technique most similar to Sissaoui and Koclas, involving convergence rates and solution results.  However, no comprehensive analysis of iteration techniques exists.
\tcr{last sentence is a bit vague}

@@

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Investigate iteration convergence for previously implemented iterative schemes and newly conceived one described in \sct{sect:inv_iter}.
\item Verify IQS method with several low and high order time discretization schemes.
\item Implement step doubling time adaptation with IQS and analyze its performance compared to implicit discretization of the flux equations.
\item Apply temperature feedback with IQS and analyze its performance with multiphysics benchmarks.
\item Implement IQS into the Rattlesnake framework at INL.
\item Perform testing with IQS to benchmarks including TWIGL and LRA. \tcr{what about the LMR benchmark? needed for paper}
\end{enumerate}

>>>>

These techniques are by no means an exhaustive list of the possible iteration techniques for IQS. Dulla et al. in \cite{Dulla2008} does an in depth analysis of the fixed point iteration technique most similar to Sissaoui and Koclas, involving convergence rates and solution results.  However, no comprehensive analysis of iteration techniques exists, comparing both Newton and fixed-point convergence rates.

@@

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Investigate iteration convergence for previously implemented iterative schemes and newly conceived one described in \sct{sect:inv_iter}.
\item Verify IQS method with several low and high order time discretization schemes.
\item Implement step doubling time adaptation with IQS and analyze its performance compared to implicit discretization of the flux equations.
\item Apply temperature feedback with IQS and analyze its performance with multiphysics benchmarks.
\item Implement IQS into the Rattlesnake framework at INL.
\item Perform testing with IQS to benchmarks including TWIGL, LRA, and LMW.
\end{enumerate}
